\speculake: Hiding Malware in Speculative Execution

### 2018-05-08 paper/conclusion.tex

In this paper we present \speculake, a model for hiding computation in speculative 
execution that is fundamentally different than modern methods of obfuscating 
computation. Through a series of experiments we have classified the 
capabilities and limitations of this speculative primitive and demonstrated 
various example applications. The flexibility in these applications stemming 
from the general computation permitted speculatively allows for emulation, 
transparent and remote communication, and process level data encryption.  
As a result current analysis techniques for detecting process cooperation, 
and describing the behavior of program
binaries are no longer definitively reliable.

Given the parameters of the speculative primitive described in this work and
the benefits that speculative execution provides to an attacker, the 
feasability of an \speculake exploit is unfortunately high and is not limited 
to data side-channels or process isolation violations. The speculative primitive 
developed in this work not only provides a guarded form of 
computation, but also enables cryptographic protection against current
analysis and debugging techniques.

>>>>

In this paper we have presented \speculake, a model for hiding computation in
speculative execution that is fundamentally different than modern methods of
obfuscating computation. Through a series of experiments we have classified the
capabilities and limitations of this speculative primitive and demonstrated
various example applications. We have demonstrated the widely varying
capabilities of speculative execution, in particular showing that it allows for
arbitrary computation from a Turing Machine, emulation, transparent and remote
communication, and process level data encryption. As a result current analysis
techniques for detecting process cooperation, and describing the behavior of
program binaries are no longer definitively reliable.

Given the benefits that speculative execution provides to an attacker and the
ease of such an attack, the feasibility of an \speculake exploit is high and is
not limited to data side-channels or process isolation violations, as was
originally thought in the wake of Spectre. The speculative primitive developed
in this work not only provides a guarded form of computation, but also enables
cryptographic protection against current analysis and debugging techniques.
